### 2022-05-23 main/chapter_2ljets.tex
write rjr summary caption

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
    \caption{$2\ell$}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
    \caption{$3\ell$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.99\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
    \caption{$\twoljets$}
\end{subfigure}
\caption{%
\TODO{summary plots with the previous 2/3l excesses and $\twoljets$.}
\TODO{reproduced from / made by the RJR team}
}
\label{fig:2ljets_signal_examples}
\end{figure}

>>>>

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
    \caption{$2\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
    \caption{$3\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.8\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
    \caption{$\twoljets$ RJR~\cite{atlas2022searches}}
\end{subfigure}
\caption{%
Summary plots for RJR analyses:
(a) and (b)~two- and three- lepton selections respectively reproduced
from~\cite{atlas_rjr_23l_SUSY_2017_03},
(c)~all regions from the $\twoljets$ RJR search~\cite{atlas2022searches}.
Note the excesses in
$\mathrm{SR}2\ell\_\mathrm{Low}$ and $\mathrm{SR}2\ell\_\mathrm{ISR}$ of (a),
and in
$\mathrm{SR}3\ell\_\mathrm{Low}$ and $\mathrm{SR}3\ell\_\mathrm{ISR}$ of (b).
\textit{Sub-figure (c) was made by the RJR team.}
}
\label{fig:2ljets_signal_examples}
\end{figure}
